%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Matthew}{Maisak}
\position{MD Candidate{\enskip\cdotp\enskip}Neuroscientist}
\address{521 Prospect St. Apt 2 New Haven, CT 06511 USA}

\mobile{(+1) 314-239-0571}
\email{matt.maisak@gmail.com}
%\homepage{www.posquit0.com}
%\github{posquit0}
\linkedin{matthewmaisak}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Roivant Sciences}
  {Viaduktstrasse 8\\4051 Basel\\Switzerland}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Business Development}
% How the letter is opened
\letteropening{\\Dear Madam, Dear Sir,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Matthew Maisak~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

Every day promising molecular candidates are sidelined because they lack proper funding and oversight to be developed into life changing medicines. We need innovative visionaries who develop solutions to both recognize effective molecules and bring them to market in a timely and efficient manner. Roivant recognized the need to disrupt the status quo through an innovative business model allowing for both nimble drug development and the economies of scale of larger companies. I am excited to help Roivant catalyze innovation through asset valuation with my analytical rigor, deep scientific expertise, and intense work ethic.

Business Development demands a deep knowledge of the life sciences coupled with outstanding business acumen and a collaborative spirit enabling effective teamwork. My life science expertise stems from both my academic research and my biotech experience. After completing my bachelor’s degree in biology, I moved to Munich and the Max Planck Institute of Neurobiology for my doctoral work. During my PhD, I worked on different projects in several capacities, from team player to project leader. For my main doctoral project, which resulted in a fundamental discovery in the field of motion vision and was published in the journal \textit{Nature}, I was awarded the “Young Scientist of the Year” award. Leaving the lab, I transitioned to the Roche Global Leadership development program, where I was given leadership responsibility from the beginning, managing my own projects dealing with strategic change management. During my tenure with Roche, I focused on simplifying and prioritizing my work and engaging my colleagues by listening, conveying my genuine interest, and explaining my perspective.  With this strategy, my projects and project teams enjoyed success, gaining the attention of senior management throughout the division. For one initiative, dealing with Partner Management, we received the go ahead from the leadership team to implement our holistic partner management concept and accompanying organizational changes. These measures led to increased satisfaction from both internal stakeholders, who now know exactly what their role is, and our external partners, who now know what they can expect from us and who to contact. Additionally, we realized a 10\% decrease in the management costs of our partnerships through streamlining processes and aligning earlier. 

Despite this success, there was a cultural divide between myself and such a large, bureaucracy laden corporation. This was a valuable experience and I learned a lot, but I was hungry for the opportunity to make a real difference. Passionate about having a direct clinical impact on patients' lives, I enrolled in Yale School of Medicine to pursue my MD. However, I quickly realized the potential influence you could have as a clinician is limited to patients you treat. I am eager for a faster, more results driven environment: a "no politics" culture of pure meritocracy, where you work hard and are judged on the quality of that work.  At a fast paced, streamlined company like Roivant, I will have the opportunity to push hundreds of molecules forward and dozens across the finish line.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}